\section{Results}
\label{sec:results}
% When reporting computational or measurement results, always report the mean (average value) along with a measure of variability (standard deviation(s) or standard error of the mean).
% \todo[inline]{Show evidence to support the claims from the introduction}

The table below summarizes the best public Kaggle scores we achieved in our implementations.

\begin{center}
 \begin{tabular}{| l | c|} 
 \hline
  Algorithm & Score \\ [0.5ex] 
 \hline\hline
 \ac{KNN} & 1.12769 \\ 
 \hline
 \ac{SVD} & 1.00636 \\
 \hline
 \ac{ALS} & 1.04141 \\
 \hline
 \ac{EDP} with \ac{SGD}, LR = 0.1, k = 17 & 1.03843 \\
 \hline
 \ac{EDP} with \ac{SGD}, adaptive LR & 0.97967 \\
 \hline
 \ac{EDP} with \ac{SGD}, adapt. LR, k $\in$ [8,17] & 0.97728 \\
 \hline
 \ac{EDP} with Adam, high batchsize & 0.98459 \\
 \hline
 \ac{EDP} with Adam, low batchsize & 0.98056 \\
 \hline
 \ac{EDP} with Adam, averaging all batchsizes & 0.97781 \\
 \hline
 
 BACF & 0.97438 \\
 \hline
\end{tabular}
\end{center}

We have found that \ac{EDP} combined with simple \ac{SGD}, where the \ac{LR} and k is fixed, already outperforms \ac{ALS} and \ac{KNN}. SVD performed better, however the potential for further improvement appeared to be more limited. Using EDP with SGD combined with an adaptive \ac{LR}, as described in Section \ref{sec:sgd_lr}, improves the score significantly, outperforming SVD. Using both an adaptive \ac{LR} and averaging over $k$, as explained in Section \ref{sec:sgd_k}, improved the score further.
The score for \ac{EDP} in combination with Adam is comparable to the score obtained from optimizing the \ac{EDP} with \ac{SGD} approach. Thus, it also outperforms all baseline algorithms. 
Combining the scores of results obtained from setting different batch sizes in \ac{EDP} with Adam resulted in an even better score and was even less prone to overfitting.
We have found that combining the results from the two approaches, EDP with SGD with an adaptive \ac{LR} and multiple k values and EDP with Adam using a low batch size, using bootstrap aggregation (BACF), as described in Section \ref{sec:bagging}, lead to the highest score improvement, resulting in a score of 0.97438.